Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-09 paper.tex
Minor fixes

\usepackage{titlesec}
\titleformat{\chapter}
  {\normalfont\LARGE\bfseries}{\thechapter}{1em}{}
\titlespacing*{\chapter}{0pt}{3.5ex plus 1ex minus .2ex}{2.3ex plus .2ex}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref} 
\usepackage{xcolor} 
\usepackage{ulem}

@@

    \begin{abstract} Text of abstract.  
    \end{abstract} 
    \tableofcontents
    \chapter{Introduction}
        In recent years, the volume of neuroimaging data acquired has exceeded
        both the storage and computation capacity of a standard research 
        lab workstation. With the advancement of data sharing technologies, 
        this data has been made widely available, however, accessibility to 
        such data remains limited due to infrastructural demands and lack of 
        performant software. Even with powerful infrastructure, such as High
        Performance Computing (HPC) infrastructure, software configured to 
        efficiently use resources is required to make execution time manageable
        . Ensuring efficient processing of data is 
        complex and limits accessibility to researchers with little programming 
        knowledge. Existing neuroimaging workflow engines primarily rely on HPC
        resource managers for performance and are therefore not well suited for
        BigData processing. As a result, frameworks for the efficient 
        processing of Big neuroimaging Data need to be developed\tristan{Add a sentence to transition from 'frameworks for efficient processing' to 'workflow engines'}

@@

            \section{Data structures}

@@

        \section{Filesystems}\label{fs}

@@

            \subsection{Strategies}
                \subsubsection{in-memory computing}
                    Random Access Memory (RAM) is the fastest memory available
                    to workflow engines. BigData frameworks, such as Spark and 
                    Dask, leverage this feature by maintaining data in memory 
                    between tasks rather that saving them to local disk or 
                    shared memory which may incur significant overhead.

@@

            To address the importance of provenance tracking for scientific 
            workflows several workflow engines adapted strategies to capture 
            provenance metadata. Some leverage the W3C PROV specification (e.g.
            Nipype, FastR, Taverna), while others may chose to use NIDM (e.g. 
            SPM). Big Data frameworks, such as Dask and Spark utilize data lineage
            to record their provenance. Other scienific workflow engines prefer 
            to record provenance in a custom format.

@@

    \addcontentsline{toc}
        {chapter}{Bibliography} 
        \bibliographystyle{ieeetr}
        \bibliography{bibliography}
\end{document}

>>>>

\usepackage{titlesec}
\titleformat{\chapter}
  {\normalfont\LARGE\bfseries}{\thechapter}{1em}{}
\titlespacing*{\chapter}{0pt}{3.5ex plus 1ex minus .2ex}{2.3ex plus .2ex}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref} 
\usepackage{xcolor} 
\usepackage{ulem}                     
\usepackage{graphicx} 
\usepackage{rotating}

@@

    \begin{abstract}

    \end{abstract} 
    \tableofcontents
    \chapter{Introduction}
        In recent years, the volume of neuroimaging data acquired has exceeded
        both the storage and computation capacity of a standard research 
        lab workstation. With the advancement of data sharing technologies, 
        this data has been made widely available, however, accessibility to 
        such data remains limited due to infrastructural demands and lack of 
        performant software. Even with powerful infrastructure, such as High
        Performance Computing (HPC) infrastructure, software configured to 
        efficiently use resources is required to make execution time manageable
        . Ensuring efficient processing of data is 
        complex and limits accessibility to researchers with little programming 
        knowledge. Existing neuroimaging workflow engines primarily rely on HPC
        resource managers for performance and are therefore not well suited for
        BigData processing. As a result, frameworks for the efficient 
        processing of Big neuroimaging Data need to be developed\tristan{Add a sentence to transition from 'frameworks for efficient processing' to 'workflow engines'}

@@

            \section{Data structures}\label{ds}

@@

        \section{Data-centric optimizations}\label{fs}

@@

            \subsection{Strategies}
                \subsubsection{In-memory computing}
                    Random Access Memory (RAM) is the fastest memory available
                    to workflow engines. BigData frameworks, such as Spark and 
                    Dask, leverage this feature by maintaining data in memory 
                    between tasks rather that saving them to local disk or 
                    shared memory which may incur significant overhead.

@@

            To address the importance of provenance tracking for scientific 
            workflows several workflow engines adapted strategies to capture 
            provenance metadata. Some leverage the W3C PROV specification (e.g.
            Nipype, FastR, Taverna), while others may chose to use NIDM-results (e.g. 
            SPM). Big Data frameworks, such as Dask and Spark utilize data lineage
            to record their provenance. Other scienific workflow engines prefer 
            to record provenance in a custom format.

@@

    \begin{sidewaysfigure}[!p]
        \centering
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Figures/summary.pdf}
        \caption{Summary table comparing the 17 workflow engines on four axes:
        workflow composition, performance, portability and reproducibility.}
    \end{sidewaysfigure} 
    \addcontentsline{toc}
        {chapter}{Bibliography} 
        \bibliographystyle{ieeetr}
        \bibliography{bibliography}
\end{document}
